\section{Re-Interviewing Clients}
I re-interviewed the clients and asked them for their opinion on the final product. These are some of the responses, I received:
\\
The first student, Nitish Bala said, \textit{"The library is extremely intuitive to use and manipulating with data-structures such as matrices and volumes is very easy to do. The optimisation methods also work well and it is very easy to define your own optimisation techniques. Overall, I think this library is easy to use and making dense nets has never been any easier than this."}
\bigbreak
The second student, Basim Khajwal said, \textit{"The library is easy to use and offers a variety of optimisation techniques. One particular part, I like a lot about this library is that it allows the user to define their own layers, which I think is a big plus. Overall, I think this library is the perfect library to go to for a beginner, if they would like to get a hands on intro to machine learning."}
\bigbreak
The third student, Taha Rind said, \textit{"I like the design of this library as it makes the library very obvious to use. I quite like the fact that making a simple dense network can be done in 5 lines of code, which makes this library appealing to use."}
\bigbreak
The fourth student, Mujahid Mamaniat said, \textit{"Making a neural network including a CNN is very easy to do, as creating a network only requires setting the parameters for each layer. Another aspect I like about the library is that although it offers many features such as enabling users to create their own layers, optimisers, activation functions it doesn't sacrifice out on the design of the software like many other ML libraries out there."}
\bigbreak
Finally, Jamie Stirling said, \textit{"I like the way the library has an extra focus on dense nets as this is what many libraries are lacking. I also like the way the library allows users to create their own activations and loss functions, without making the library too difficult to work with. Overall, I think this library is perfect for a beginner as it is not complicated but at the same time offers many features which might interest the user even more."}
\bigbreak

Therefore, it is quite obvious from these feed-backs that the library has been successful in delivering a machine learning library for beginners.