\section{Aims \& Objectives}
It is clear, that although there are many machine learning libraries, many of these are out of reach for A level students, due to their very limited knowledge of AI and expertise. Therefore, my project will be focused on making a machine learning library that is focused only on deep-learning and will be made specifically for VB users. By having a specific target market, I will be able to clearly set my Aims and objectives to fulfil the users needs.
\subsection{My Core Aims}
The core aims that I would like my project to meet are:
\begin{enumerate}
    \item The user can manipulate with matrices by joining two matrices together, splitting a given matrix, iterate through the columns of a matrix or its values and applying a onehot encoding function to a given matrix
    \item The user can multiply, add, subtract and transpose a given matrix.
    \item The user can multiply, add, subtract and transpose a list of matrices together, i.e volumes.
    \item The user can create their own Dense Neural Networks.
    \item The user has an option in which activation function they would like to use and also allow the user to experiment with their own activation functions.
    \item The user can tune the hyper parameters, such as the learning rate, number of neurons in a layer, number of layers and loss function.
    \item The user can train the network using a back-propagation algorithm.
    \item The gradient descent algorithms should implement stochastic gradient descent, batch gradient descent as well as mini-batch gradient descent.
    \item The user can view the weights of the network i.e learned parameters of the network
    \item The user can view the gradients for a specific layer in a dense-net, given the gradients for the layer above.
    \item The user can add convolutional layers to their network, which they can tune by changing the hyper parameters such as the kernel dimensions, layer activation and kernel strides. 
\end{enumerate}
\subsection{Desired Objectives}
\begin{enumerate}
    \item The user can choose from a wide range of optimisation algorithms such as momentum, RMS and Adam to train their dense networks
    \item The user can define their own back propagation algorithms to train their neural networks
    \item The user can define their own layers
\end{enumerate}